Towards a Classification of Sporadic $j$-invariants

### 2023-04-05 TeX/draft.tex
Updates from Overleaf

\usepackage{amsmath,amsthm,amssymb}

@@

\renewcommand{\epsilon}{\varepsilon}
\renewcommand{\phi}{\varphi}
\renewcommand{\theta}{\vartheta}

\renewcommand\labelenumi{(\theenumi)}
\renewcommand{\theenumi}{\roman{enumi}}

@@

>>>>

\usepackage{amsmath,amsthm,amssymb}
% \usepackage{algorithm2e}

@@

\renewcommand{\epsilon}{\varepsilon}
\renewcommand{\phi}{\varphi}
\renewcommand{\theta}{\vartheta}
\newcommand{\Supp}{\operatorname{Supp}}
\renewcommand\labelenumi{(\theenumi)}
\renewcommand{\theenumi}{\roman{enumi}}

@@

\section{Reduce Level}
\noindent \textbf{Input:} Non-CM elliptic curve $E/\Q$\\
\textbf{Output:} Finite set of positive integers $\mathcal{I}_1$ such that any isolated point $x \in X_1(n)$ with $j(x) =j(E)$ maps under the natural projection map to an isolated point on $X_1(d)$ for $d \in \mathcal{I}_1$.
\begin{theorem}
Let $E/\Q$ be a non-CM elliptic curve, and let $\rho_E$ denote the adelic Galois representation of $E$. Let $M_E$ be any positive integer such that 
\[
\im \rho_E=\pi^{-1}(\im \rho_{E, M_E}).
\]
Then for any $x \in X_1(n)$ with $j(x)=j(E)$ we have $\deg(x)=\deg(f)\cdot \deg(f(x))$, where $f: X_1(n) \rightarrow X_1(\gcd(n,M_E))$ denotes the natural map. It follows that:
\begin{enumerate}
\item If $x$ is $\mathbb{P}^1$-isolated, then $f(x)$ is $\mathbb{P}^1$-isolated.
\item If $x$ is AV-isolated, then $f(x)$ is AV-isolated.
\item If $x$ is sporadic, then $f(x)$ is sporadic.
\end{enumerate}
\end{theorem}

\begin{proof}
This follows from the arguments in Section 5.3 of BELOV (see Remark 5.5 in particular) and Theorem 4.3.
\end{proof}

Let $S_E=\{2,3\} \cup \{\ell : \rho_{E,\ell^{\infty}}(\Gal_{\Q}) \neq \GL_2(\Z_{\ell})\}$. Let $M_E=M_1\cdot M_2$ where $\Supp(M_1) \subseteq S_E$ and $\Supp(M_2) \cap S_E =\emptyset$.

\begin{corollary}
Let $E/\Q$ be a non-CM elliptic curve, and let $\rho_E$ denote the adelic Galois representation of $E$. 
Then for any $x \in X_1(n)$ with $j(x)=j(E)$ we have $\deg(x)=\deg(f)\cdot \deg(f(x))$, where $f: X_1(n) \rightarrow X_1(\gcd(n,M_1))$ denotes the natural map. It follows that:
\begin{enumerate}
\item If $x$ is $\mathbb{P}^1$-isolated, then $f(x)$ is $\mathbb{P}^1$-isolated.
\item If $x$ is AV-isolated, then $f(x)$ is AV-isolated.
\item If $x$ is sporadic, then $f(x)$ is sporadic.
\end{enumerate}
\end{corollary}

\begin{proof}
This should follow from BELOV Proposition 5.7.
\end{proof}

Main idea beyond this: Let $m$ be the product of the primes in $\Supp(M_1)$. By Proposition 5.8 in BELOV, it suffices to replace $M_1$ in the corollary above with the level of the $m$-adic Galois representation. This should be the main point of the ``ReducedLevel" operation: to compute this level. Note in particular we do not need to add in 2 and 3 if they were not already in $\Supp(M_E)$.

\section{Compute Degree}

\noindent \textbf{Input:} $\mathcal{I}_1$ from step 1\\
\textbf{Output:} For each $d \in \mathcal{I}_1$, compute degree(s) of closed point on $X_1(n)$ associated to $E$. Return ???

\begin{proposition}
Let $E/\Q$ be a non-CM elliptic curve and $n \in \mathbb{Z}^+$. If $\im \rho_{E,n} \cong G \leq \GL_2(\Z/n\Z)$, then ...
\end{proposition}

\section{Riemann-Roch}

\noindent \textbf{Input:} Output from step 2\\
\textbf{Output:} Smaller list of pairs to check

\begin{lemma}
Let $C$ be a curve over a number field $k$ with genus $g$. If $x \in C(\overline{k})$ is a closed point with degree
$\geq g+1$, then $x$ is not $\mathbb{P}^{1}$-isolated.
\end{lemma}

\begin{proof}
This is Lemma 13 in revision of B., Gill, Rouse, Watson.
\end{proof}

\section{Remaining Cases}

Filip's arguemnts
